Batch, Off-policy and Model-free Apprenticeship Learning

### 2013-08-09 Manuscrit/titlepage.tex
Envoi aux trois

\noindent \textbf{Membres du jury}\noindent\\ \noindent
\begin{tabularx}{18cm}{p{3.5cm}p{4cm}p{10.5cm}}
Directeur de thèse & Dr. Yann Guermeur &\small{Directeur de recherche, Equipe ABC, Loria-CNRS -- Nancy}\\
Co-directeur de thèse &Dr. Matthieu Geist &\small{Directeur de recherche, Equipe IMS-MaLIS, Supélec -- Metz}\\
 Rapporteurs&Dr. Rachid Alami &\small{Directeur de recherche, LAAS /  CNRS -- Toulouse}\\
 &Prof. Brahim  Chaib-draa&\small{Professeur, DAMAS, Université Laval -- Québec}\\ 
Examinateurs &Prof. Sylvain Contassot-Vivier&\small{Professeur, Loria-Université de Lorraine -- Nancy}\\
&Dr. Guillaume Laurent&\small{Maître de conférences, Institut FEMTO-ST / ENSMM -- Besançon}\\
 &Dr. Manuel Lopes&\small{Chargé de recherche, Equipe Flowers, INRIA -- Bordeaux}\\
&Dr. Olivier Pietquin &\small{Directeur de recherche, Equipe IMS-MaLIS / UMI 2958, Supélec -- Metz}
\end{tabularx}

>>>>

\noindent \textbf{Membres du jury}\noindent\\ \noindent
\begin{tabularx}{18cm}{p{3.5cm}p{4cm}p{10.5cm}}
Directeur de thèse & Dr. Yann Guermeur &\small{Directeur de recherche, Equipe ABC, Loria-CNRS -- Nancy}\\
Co-directeur de thèse &Dr. Matthieu Geist &\small{Enseignant-chercheur, Equipe IMS-MaLIS, Supélec -- Metz}\\
 Rapporteurs&Dr. Rachid Alami &\small{Directeur de recherche, LAAS /  CNRS -- Toulouse}\\
 &Prof. Brahim  Chaib-draa&\small{Professeur, DAMAS, Université Laval -- Québec}\\ 
Examinateurs &Prof. Sylvain Contassot-Vivier&\small{Professeur, Loria-Université de Lorraine -- Nancy}\\
&Dr. Guillaume Laurent&\small{Maître de conférences, Institut FEMTO-ST / ENSMM -- Besançon}\\
 &Dr. Manuel Lopes&\small{Chargé de recherche, Equipe Flowers, INRIA -- Bordeaux}\\
&Dr. Olivier Pietquin &\small{Enseignant-chercheur, Equipe IMS-MaLIS / UMI 2958, Supélec -- Metz}
\end{tabularx}
